A Method for the Spectroscopic Inference of Stellar Parameters

### 2014-06-30 tex/paper.tex
new input file
added nocov ability

\section{Introduction \label{sec:intro}}

@@

We adopt a somewhat analogous approach to deal with this issue, but cast it internal to the 
modeling framework to appropriately propagate the uncertainty introduced by additional degrees of 
freedom in the model.  The residual calibration errors are treated as an explicit contribution to 
the model spectrum, enabling us to explore the distribution of possible calibrations (see 
Section~\ref{subsec:MCMC}) and then eventually marginalize out the associated nuisance parameters.  
In essence, the inferences for the relevant stellar parameters will properly account for the 
underlying uncertainty in the calibration process.  This is achieved in practice by distorting the 
model spectrum with a (low-order) Chebyshev polynomial \citep[e.g.,][]{eisenstein06,koleva09}, 
\begin{equation}
\vM(\vt, \vT_{\rm cheb}) = \vM(\vt) \times \sum_n c_n \, T_n,
\end{equation}
where $T_n$ are the standard Chebyshev functions of order $n$ and the coefficients are treated as a
set of nuisance (hyper-)parameters, $\vT_{\rm cheb} = \{c_n\}^{\rm order}$, for each available 
spectral order in the dataset.  With judicious priors on $\vT_{\rm cheb}$, we can ensure that the 
unintended treatment of real spectral features (e.g., broad, deep molecular bands) as calibration 
artifacts is negligible (see Secton~\ref{sec:examples} for examples).  The lowest-order (scaling) 
coefficient, $c_0$, is by its nature degenerate with the solid angle parameter, $\Omega$.  
Therefore, we enforce an additional constraint by requiring that the mean of the polynomial is 
unity.  For data with a single spectral order, this means setting $c_0 = 1$.  If the goal is to 
model multiple spectral orders, we assign $c_0 = 1$ in an arbitrary order as an anchor, but permit 
the $c_0$ values in other orders to be different (as necessary).  It is worth noting that this 
formalism can, in principle, be extended to develop models for completely uncalibrated spectra, 
rather than the residual calibration mismatches as described here (with a suitable relaxation of 
the priors on $\vT_{\rm cheb}$).  Figure \ref{fig:chebyshev} offers a practical demonstration of how 
these nuisance parameters are applied.

@@

\begin{figure*}[!htb]
\begin{center}
  \includegraphics[draft, width=5in]{figs/stellar_triangle.png}
  \caption{The posterior probability function of the stellar parameters for WASP-14, an F star, as explored by the MCMC Gibbs sampler. These stellar parameters are marginalized over the Chebyshev and noise parameters. Figure generated with \texttt{triangle.py} \citep{foreman-mackey14}.
}
\label{fig:stellar_posterior}
\end{center}
\end{figure*}

@@

\section{Worked Examples \label{sec:examples}}
Here are some ideas of which tests we might want to show.

@@

\section{Discussion \label{sec:discussion}}

\section{Conclusion \label{sec:conclusion}}

>>>>

\section{Introduction}
\label{sec:intro}

@@

We adopt a somewhat analogous approach to deal with this issue, but cast it internal to the 
modeling framework to appropriately propagate the uncertainty introduced by additional degrees of 
freedom in the model.  The residual calibration errors are treated as an explicit contribution to 
the model spectrum, enabling us to explore the distribution of possible calibrations (see 
Section~\ref{subsec:MCMC}) and then eventually marginalize out the associated nuisance parameters.  
In essence, the inferences for the relevant stellar parameters will properly account for the 
underlying uncertainty in the calibration process.  This is achieved in practice by distorting the 
model spectrum with a (low-order) Chebyshev polynomial \citep[e.g.,][]{eisenstein06,koleva09}, 
\begin{equation}
\vM(\vt, \vT_{\rm cheb}) = \vM(\vt) \times \sum_n c_n \, T_n,
\end{equation}
where $T_n$ are the standard Chebyshev functions of order $n$ and the coefficients are treated as a
set of nuisance (hyper-)parameters, $\vT_{\rm cheb} = \{c_n\}^{\rm order}$, for each available 
spectral order in the dataset.  With judicious priors on $\vT_{\rm cheb}$, we can ensure that the 
unintended treatment of real spectral features (e.g., broad, deep molecular bands) as calibration 
artifacts is negligible (see Section~\ref{sec:examples} for examples).  The lowest-order (scaling) 
coefficient, $c_0$, is by its nature degenerate with the solid angle parameter, $\Omega$.  
Therefore, we enforce an additional constraint by requiring that the mean of the polynomial is 
unity.  For data with a single spectral order, this means setting $c_0 = 1$.  If the goal is to 
model multiple spectral orders, we assign $c_0 = 1$ in an arbitrary order as an anchor, but permit 
the $c_0$ values in other orders to be different (as necessary).  It is worth noting that this 
formalism can, in principle, be extended to develop models for completely uncalibrated spectra, 
rather than the residual calibration mismatches as described here (with a suitable relaxation of 
the priors on $\vT_{\rm cheb}$).  Figure \ref{fig:chebyshev} offers a practical demonstration of how 
these nuisance parameters are applied.

@@

\begin{figure*}[!htb]
\begin{center}
  \includegraphics[width=5in]{figs/stellar_triangle_Kurucz.png}
  \caption{The posterior probability function of the stellar parameters for WASP-14, an F star, as explored by the MCMC Gibbs sampler. These stellar parameters are marginalized over the Chebyshev and noise parameters. Figure generated with \texttt{triangle.py} \citep{foreman-mackey14}.
}
\label{fig:stellar_posterior}
\end{center}
\end{figure*}

\begin{figure*}[!htb]
\begin{center}
  \includegraphics[width=5in]{figs/stellar_triangle_WASP14_Kurucz.png}
  \caption{The posterior probability function of the stellar parameters for WASP-14, logg fixed to match \citep{torres12}. Using three orders, Kurucz grid. Same assumptions.}
\label{fig:stellar_posterior_logg}
\end{center}
\end{figure*}

@@

\section{Worked Examples}
\label{sec:examples}
Here are some ideas of which tests we might want to show.

@@

\section{Discussion}
\label{sec:discussion}

\section{Conclusion}
\label{sec:conclusion}
